---
title: "Worksheet 8 Solution"
author: "Fred Azizi"
date: "2022-10-26"
output: pdf_document
---


1. Acme Corporation's helpdesk gets 4 calls per day on average. They think the number of calls follows a Poisson distribution. 

> a. What is the probability that they get 3 calls or less on a given day?

> b. What is the probability that they get no calls on given day?

> c. What is the probability that they get exactly 3 calls?

> d. What is the expected number of calls in a week? 

> e. What is the standard deviation for calls in a day?


> **\underline{Answer:}**

> (a) Using table: $P[x \leqslant 3]=0.4335$.

> (b) Using table:

$$ 
P[x=0]=P[x \leqslant 0]=0.0183 
$$ 

>> Direct calculation:

$$ 
P[x=0]=\frac{e^{-4} 4^0}{0!}=0.01831564
$$ 

> (c) Using table: $P[x=3]=P[x \leqslant 3]-P[x \leqslant 2]=0.4335-0.2381=0.1954$. 

>> Direct calculation: $P[x=3]=\frac{e^{-4}4^3}{3!}=0.1953668$ 


> (d) Let $Y=\#$ calls per week on average. Then, $Y=7X$. $E(Y)=E(7X)=7E(X)=7\times4=28$.

> (e) $V(X)=\mu=4 \rightarrow SD(x)=\sqrt{4}=2$. 


\newpage

2. The number of flaws in an optic fiber cable follows a Poisson Distribution. The average number of flaws in $50 \mathrm{~m}$ is $1.5$. Let $X=$ average number of  flaws in $50 \mathrm{~m}$.

> a. What is the probability of exactly 2 flaws in $100 \mathrm{~m}$ ?

> b. What is the probability of 3 flaws or less in $150 \mathrm{~m}$ ?

> **\underline{Answer:}**

> (a) Let $Y=$ average number of  flaws in $100 \mathrm{~m}$. $Y=2X$. $E(Y)=2E(X)=3$. Using table:

$$
P(Y=2)=P(Y \leqslant 2)-P(Y \leqslant 1)=0.4232-0.1991=0.2241
$$

>> Or, using direct calculation:

$$
P(Y=2)=\frac{e^{-3}3^2}{2!}=0.2240418
$$

> (b) Let $Z=$ average number of  flaws in $150 \mathrm{~m}$. $Z=3X$. $E(Z)=3E(X)=4.5$. Using table:

$$
P(Y \leqslant 3)=0.3423
$$

\newpage

3. $X$ is a Uniformly distributed random variable that has maximum and minimum values of 10 and 50.

> a. What is the density function and its graph?

> b. Calculate the mean of $X$.

> c. Calculate $P[10<X<20]$ and mark the corresponding area on the graph from (a).

> d. Calculate $P[25<X<45]$ and mark the corresponding area on the graph from (a).

> e. Find $P[X=22.5]$.

> **\underline{Answer:}**

> (a) $f(x)=\frac{1}{b-a}=\frac{1}{50-10}=\frac{1}{40}$.

```{r,echo=F}
library(ggplot2)

a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()
```

> (b) $\mu=\frac{a+b}{2}=\frac{10+50}{2}=30$.

> (c) Blue area= $(20-10)\times \frac{1}{40}=\frac{1}{4}=0.25$.

```{r, echo=F}
a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()+
    annotate("rect", 
           xmin = 10, 
           xmax = 20,
           ymin = 0,
           ymax = 1/40,
           fill = "red", alpha=0.5) 

```


> (d) Red area= $(45-25)\times \frac{1}{40}=\frac{1}{2}=0.5$.

```{r, echo=F}
a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()+
    annotate("rect", 
           xmin = 25, 
           xmax = 45,
           ymin = 0,
           ymax = 1/40,
           fill = "blue", alpha=0.5) 

```

> (e) This is a continuous RV. Hence, P[X=22.5]=0$.


\newpage

1. Calculate the following Probabilities from using a standard Normal distribution, $Z$ $\sim$ N(0,1).


> a. $P[Z < 0]$.

>> A: Using table, $P[Z < 0]=0.5$.

> b. $P[Z < -1.5]$.

>> A: Using table, $P[Z < -1.5]=0.0668$.

> c. $P[Z > 1]$.

>> A:  $P[Z > 1]\stackrel{\text{Compliment R}}{=} 1- P[Z \leq 1]= 1- 0.8413=0.1587$.


> d. $P[Z > -1.44]$.

>> A:  $P[Z > -1.44]\stackrel{\text{Compliment R}}{=} 1- P[Z \leq -1.44]= 1- 0.0749=0.9251$.

> e. $P[Z > 3.09]$.

>> A:  $P[Z > 3.09]\stackrel{\text{Compliment R}}{=} 1- P[Z \leq 3.09]= 1- 0.9990=0.001$.

> f. $P[-0.71 < Z < 0.92]$.

>> A: $P[-0.71 < Z < 0.92]=P[Z<0.92]-P[Z<-0.71]=0.8212-0.2389=0.5823$. Why? See below:

>> This is what we want:

```{r, echo=F,out.width="70%",fig.align = 'center'}
library(ggplot2)
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "steelblue",
                xlim = c(-0.71, 0.92), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3,-0.71, 0, 0.92, 3),
                     labels = c(-3, -0.71,0, 0.92, 3),
                     limits = c(-3, 3)) 

```
>> We note that P[Z<0.92] would be the red area on this plot: 

```{r, echo=F,out.width="70%",fig.align = 'center'}
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "red",
                xlim = c(-3, 0.92), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3, 0, 0.92, 3),
                     labels = c(-3, 0, 0.92, 3),
                     limits = c(-3, 3)) 

```

>> We also note that P[Z<-0.71] would be the green area on this plot: 

```{r, echo=F,out.width="70%",fig.align = 'center'}
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "green",
                xlim = c(-3,-0.71), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3,-0.71, 0, 3),
                     labels = c(-3, -0.71,0,  3),
                     limits = c(-3, 3)) 

```

>> If I get rid of the green area in the red area, what I am left with would be the blue area. 

```{r, echo=F,out.width="70%",fig.align = 'center'}
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "green",
                xlim = c(-3,-0.71), alpha=0.5) +
  stat_function(fun = dnorm,
                geom = "area",
                fill = "steelblue",
                xlim = c(-0.71,0.92), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3,-0.71, 0, 0.92, 3),
                     labels = c(-3, -0.71,0, 0.92, 3),
                     limits = c(-3, 3)) 

```

> g. $P[-1.5 < Z < -1.44]$.

>> A: $P[-1.5 < Z < -1.44]=P[Z<-1.44]-P[Z<-1.5]=0.0749-0.0668=0.0081$.

> h. $P[Z < -0.71$ or $Z > 0.92]$.

>> A: $P[Z < -0.71 \cup Z > 0.92] = P[Z < -0.71] + P[Z > 0.92] -P[Z < -0.71 \cap Z > 0.92]$. There is no common Z in the intersection, i.e $P[Z < -0.71 \cap Z > 0.92]=0$. Hence:

\begin{align}
P[Z < -0.71 \cup Z > 0.92] &= P[Z < -0.71] + P[Z > 0.92] \notag\\
&= P[Z < -0.71]+1- P[Z \leq 0.92] \notag\\
&=0.2389+1-0.8212\notag\\
&= 0.4177 \notag
\end{align}