---
title: "Chapter 8 (part 2) and Chapter 9 (part 1)"
author: "Fred Azizi"
date: "2023-11-21"
output: 
   beamer_presentation:
     theme: "Frankfurt"
     colortheme: "crane"
header-includes:
- \usepackage{xcolor}
- \usepackage{adjustbox}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Quick review (1)


* Exponential Random Variable:
   + Defined by parameter $\lambda$.
   + $\mu=\sigma=\frac{1}{\lambda}$.
   + $P(X<x)=1-e^{-\lambda x}$ 
   + $P\left(x_1<X<x_2\right)=P\left(X<x_2\right)-P\left(X<x_1\right)=e^{-\lambda x_1}-e^{-\lambda x_2}$
   + relationship between Poisson RV and Exp RV, read [this](https://medium.com/swlh/the-link-between-poisson-and-exponential-distribution-817e92344d1b).
   
```{r, echo=F, fig.align='center', out.width="50%"}
x_lower <- 0
x_upper <- 5
 
max_height2 <- max(dexp(x_lower:x_upper, rate = 1, log = FALSE), 
                    dexp(x_lower:x_upper, rate = 2, log = FALSE),
                    dexp(x_lower:x_upper, rate = 3, log = FALSE),
                    dexp(x_lower:x_upper, rate = 0.5, log = FALSE))
 

ggplot(data.frame(x = c(x_lower, x_upper)), aes(x = x)) + xlim(x_lower, x_upper) + 
     ylim(0, max_height2) +
     stat_function(fun = dexp, args = list(rate = 0.5), aes(colour = "0.5")) + 
     stat_function(fun = dexp, args = list(rate = 1), aes(colour = "1")) + 
     stat_function(fun = dexp, args = list(rate = 2), aes(colour = "2")) + 
     stat_function(fun = dexp, args = list(rate = 3), aes(colour = "3")) + 
     scale_color_manual("Rate", values = c("blue", "green", "red", "purple")) +
     labs(x = "\n x", y = "f(x) \n", 
        title = "Exponential Distribution Density Plots \n") + 
     theme(plot.title = element_text(hjust = 0.5), 
         axis.title.x = element_text(face="bold", colour="blue", size = 12),
         axis.title.y = element_text(face="bold", colour="blue", size = 12),
         legend.title = element_text(face="bold", size = 10),
         legend.position = "right")+theme_bw()
```


## Quick review (2)

Other distributions:

* Student's $t$ distribution with parameter $\nu$ (called **"degrees of freedom"**).
   + $E(t)=0$ 
   + $V(t)=\frac{\nu}{\nu-2} \text { for } \nu>2$
* $\chi^2$ (pronounced Chi-squared) distribution  with parameter $\nu$.
   + $E\left(\chi^2_{\nu}\right)=\nu$.
   + $V\left(\chi^2_\nu\right)=2 \nu$.
   
* $F$ distribution with two parameters $\nu_1$ and $\nu_2$.
   + $E(F_{\nu_1,\nu_2})=\frac{\nu_2}{\nu_2-2} \quad \nu_2>2$ .
   + $V(F_{\nu_1,\nu_2})=\frac{2 \nu_2^2\left(\nu_1+\nu_2-2\right)}{\nu_1\left(\nu_2-2\right)^2\left(\nu_2-4\right)} \quad \nu_2>4$ 
   
   
## Quick review (3)

A lot of confusing/similar terms...What they mean??

* Population

* Sample

* Sample means

* distribution of sample vs distribution of sample means vs distribution of population

## Quick review (4)

**Central Limit Theorem**

 **The sampling distribution of the mean of a random sample drawn from any population is approximately normal for a sufficiently large sample size.**
 
 * \textcolor{red}{Mean} of distribution of the sampling mean is the same as mean of the population, $\mu_{\bar{X}}=\mu$.
 * Standard deviation of the sampling distribution (\textcolor{red}{standard error} of the mean is $\sigma_{\bar{X}}=\frac{\sigma}{\sqrt n}$.
 * $\bar{X} \sim N(\mu,\frac{\sigma}{\sqrt n})$.
 * Finite population correction for standard error: 
 $$\sigma_{\bar{X}}=\sqrt{\frac{N-n}{N-1}} \cdot \frac{\sigma}{\sqrt{n}}$$
    + Rule of thumb: Use for population that is at least 20 times larger than the sample size
