---
title: "Worksheet 7 Solution"
author: "Fred Azizi"
date: "2022-10-24"
output: pdf_document
---

1. A six-sided die is rolled 6 times. Let $X$ denote the number of times an even number showed up.

> a. What is the probability of the event happening? That is, the probability of getting an even number. 

> b. What distribution will $X$ follow? Identify the parameters.

> c. Calculate $P[X=2]$.

> d. Calculate $P[0 \leq X<3]$

> **\underline{Answer:}**

> (a) That is, the probability of getting an even number. $P(x)=\frac{1}{2}$ (for a single roll of the die).

> (b) $X \sim \operatorname{Bin}(n=6, p=0.5)$

> (c) Method 1 (using table):

$$P[x=2]=P[x \leqslant 2]-P[x \leqslant 1]=0.3438-0.1094=0.2344$$

>> Method 2 (Direct calculation):

$$P[x=2]= \binom{6}{2} 0.5^2 (1-0.5)^{6-2}=0.234375$$

> (d)
                                                                                                                           
$$                                                                                                                  \begin{aligned}
P[0 \leqslant x<3] &=P[x<3]=P[x \leqslant 2] \\
&=0.3438\\
\end{aligned}                                                                                                       $$

\newpage

2. Acme Corporation's helpdesk gets 4 calls per day on average. They think the number of calls follows a Poisson distribution. 

> a. What is the probability that they get 3 calls or less on a given day?

> b. What is the probability that they get no calls on given day?

> c. What is the probability that they get exactly 3 calls?

> d. What is the expected number of calls in a week? 

> e. What is the standard deviation for calls in a day?


> **\underline{Answer:}**

> (a) Using table: $P[x \leqslant 3]=0.4335$.

> (b) Using table:

$$ 
P[x=0]=P[x \leqslant 0]=0.0183 
$$ 

>> Direct calculation:

$$ 
P[x=0]=\frac{e^{-4} 4^0}{0!}=0.01831564
$$ 

> (c) Using table: $P[x=3]=P[x \leqslant 3]-P[x \leqslant 2]=0.4335-0.2381=0.1954$. 

>> Direct calculation: $P[x=3]=\frac{e^{-4}4^3}{3!}=0.1953668$ 


> (d) Let $Y=\#$ calls per week on average. Then, $Y=7X$. $E(Y)=E(7X)=7E(X)=7\times4=28$.

> (e) $V(X)=\mu=4 \rightarrow SD(x)=\sqrt{4}=2$. 


\newpage

3. The number of flaws in an optic fiber cable follows a Poisson Distribution. The average number of flaws in $50 \mathrm{~m}$ is $1.5$. Let $X=$ average number of  flaws in $50 \mathrm{~m}$.

> a. What is the probability of exactly 2 flaws in $100 \mathrm{~m}$ ?

> b. What is the probability of 3 flaws or less in $150 \mathrm{~m}$ ?

> **\underline{Answer:}**

> (a) Let $Y=$ average number of  flaws in $100 \mathrm{~m}$. $Y=2X$. $E(Y)=2E(X)=3$. Using table:

$$
P(Y=2)=P(Y \leqslant 2)-P(Y \leqslant 1)=0.4232-0.1991=0.2241
$$

>> Or, using direct calculation:

$$
P(Y=2)=\frac{e^{-3}3^2}{2!}=0.2240418
$$

> (b) Let $Z=$ average number of  flaws in $150 \mathrm{~m}$. $Z=3X$. $E(Z)=3E(X)=4.5$. Using table:

$$
P(Y \leqslant 3)=0.3423
$$

\newpage

4. $X$ is a Uniformly distributed random variable that has maximum and minimum values of 10 and 50.

> a. What is the density function and its graph?

> b. Calculate the mean of $X$.

> c. Calculate $P[10<X<20]$ and mark the corresponding area on the graph from (a).

> d. Calculate $P[25<X<45]$ and mark the corresponding area on the graph from (a).

> e. Find $P[X=22.5]$.

> **\underline{Answer:}**

> (a) $f(x)=\frac{1}{b-a}=\frac{1}{50-10}=\frac{1}{40}$.

```{r,echo=F}
library(ggplot2)

a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()
```

> (b) $\mu=\frac{a+b}{2}=\frac{10+50}{2}=30$.

> (c) Blue area= $(20-10)\times \frac{1}{40}=\frac{1}{4}=0.25$.

```{r, echo=F}
a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()+
    annotate("rect", 
           xmin = 10, 
           xmax = 20,
           ymin = 0,
           ymax = 1/40,
           fill = "red", alpha=0.5) 

```


> (d) Red area= $(45-25)\times \frac{1}{40}=\frac{1}{2}=0.5$.

```{r, echo=F}
a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()+
    annotate("rect", 
           xmin = 25, 
           xmax = 45,
           ymin = 0,
           ymax = 1/40,
           fill = "blue", alpha=0.5) 

```