---
title: "Worksheet 8"
author: "Fred Azizi"
date: "2022-10-31"
output: pdf_document
---

1. Calculate the following Probabilities from using a standard Normal distribution, $Z$ $\sim$ N(0,1).

> a. $P[Z < 0]$.

> b. $P[Z < -1.5]$.

> c. $P[Z > 1]$.

> d. $P[Z > -1.44]$.

> e. $P[Z > 3.09]$.

> f. $P[-0.71 < Z < 0.92]$.

> g. $P[-1.5 < Z < -1.44]$.

> h. $P[Z < -0.71$ or $Z > 0.92]$.


```{r, echo=F,out.width="70%",fig.align = 'center'}
library(ggplot2)
ggplot(data = data.frame(x = c(-3.5, 3.5)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+theme_bw()+
  scale_x_continuous(breaks = round(seq(-3.5, 3.5, by = 0.5),1)) 
```

\newpage

2. Find values of $z$ such that:

> a. The area to the left is 0.0202.

> b. The area to the left is 0.7517.

> c. The area to the right is 0.025.

> d. The area to the right is 0.3015.

```{r, echo=F,out.width="70%",fig.align = 'center'}
library(ggplot2)
ggplot(data = data.frame(x = c(-3.5, 3.5)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+theme_bw()+
  scale_x_continuous(breaks = round(seq(-3.5, 3.5, by = 0.5),1)) 
```

\newpage

3. The long term distance calls made by the employees of a company are normally distributed with a mean of $6.5$ minutes and a standard deviation of 2 minutes. 

> a. What is the probability that a call lasts less than 4 minutes? 

> b. What is the probability that a call lasts between 5 to 10 minutes. 

> c. What percentage of calls lasts more than 7 minutes?

\newpage

4. A worker earns $\$ 15$ per hour and is told that $10 \%$ of all workers make a higher wage. Assume the wage is Normally distributed with a standard deviation of 5 . What is the average wage of the company? 

\newpage

5. The manager of a gas station has observed that the times required by drivers to fill their car's tank and
pay are quite variable. In fact, the times are exponentially distributed with a mean of 7.5 minutes. 

> a. What is the probability that a transaction is completed in less than 5 minutes?

> b. What is the probability that a car can complete the transaction between 5 minutes to 10 minutes?

> c. What is the standard deviation of time until a transaction is completed?

\newpage

6. Find the mean and standard deviations:

> a. $t_5$.

> b. $\chi^2_9$.

> c. $F_{5,15}$. 

