---
title: "Worksheet 9"
author: "Fred Azizi"
date: "2023-04-11"
output: pdf_document
---

1. $X$ is a Uniformly distributed random variable that has maximum and minimum values of 10 and 50.

> a. What is the density function and its graph?

> b. Calculate the mean of $X$.

> c. Calculate $P[10<X<20]$ and mark the corresponding area on the graph from (a).

> d. Calculate $P[25<X<45]$ and mark the corresponding area on the graph from (a).

> e. Find $P[X=22.5]$.

\newpage

2. Calculate the following Probabilities from using a standard Normal distribution, $Z$ $\sim$ N(0,1).

> a. $P[Z < 0]$.

> b. $P[Z < -1.5]$.

> c. $P[Z > 1]$.

> d. $P[Z > -1.44]$.

> e. $P[Z > 3.09]$.

> f. $P[-0.71 < Z < 0.92]$.

> g. $P[-1.5 < Z < -1.44]$.

> h. $P[Z < -0.71 \text{ or } Z > 0.92]$.

```{r, echo=F,out.width="70%",fig.align = 'center'}
library(ggplot2)
ggplot(data = data.frame(x = c(-3.5, 3.5)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+theme_bw()+
  scale_x_continuous(breaks = round(seq(-3.5, 3.5, by = 0.5),1)) 
```
\newpage

3. Find values of $z$ such that:

> a. The area under the normal curve to the left is 0.0202.

> b. The area under the normal curve to the left is 0.7517.

> c. The area under the normal curve to the right is 0.025.

> d. The area under the normal curve to the right is 0.3015.

```{r, echo=F,out.width="70%",fig.align = 'center'}
library(ggplot2)
ggplot(data = data.frame(x = c(-3.5, 3.5)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+theme_bw()+
  scale_x_continuous(breaks = round(seq(-3.5, 3.5, by = 0.5),1)) 
```