---
title: "Worksheet 9 Solution"
author: "Fred Azizi"
date: "2023-04-11"
output: pdf_document
---

1. $X$ is a Uniformly distributed random variable that has maximum and minimum values of 10 and 50.

> a. What is the density function and its graph?

> b. Calculate the mean of $X$.

> c. Calculate $P[10<X<20]$ and mark the corresponding area on the graph from (a).

> d. Calculate $P[25<X<45]$ and mark the corresponding area on the graph from (a).

> e. Find $P[X=22.5]$.

> **\underline{Answer:}**

> (a) $f(x)=\frac{1}{b-a}=\frac{1}{50-10}=\frac{1}{40}$.

```{r,echo=F}
library(ggplot2)

a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()
```

> (b) $\mu=\frac{a+b}{2}=\frac{10+50}{2}=30$.

> (c) Red area= $(20-10)\times \frac{1}{40}=\frac{1}{4}=0.25$.

```{r, echo=F}
a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()+
    annotate("rect", 
           xmin = 10, 
           xmax = 20,
           ymin = 0,
           ymax = 1/40,
           fill = "red", alpha=0.5) 

```


> (d) blue area= $(45-25)\times \frac{1}{40}=\frac{1}{2}=0.5$.

```{r, echo=F}
a=10
b=50

d<-data.frame(x=c(a,b),y=c(1/40,1/40))

ggplot(d, aes(x=x,y=y))+geom_point()+geom_line() + xlim(c(a, b)) + ylim(0, 1/(b - a)) +
      labs(x = "\n x", y = "f(x) \n") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.title.x = element_text(face="bold", colour="blue", size = 12),
          axis.title.y = element_text(face="bold", colour="blue", size = 12)) +
    geom_segment(x=a, y=0, xend=a, yend=1/(b - a),linetype = "dashed") +
    geom_segment(x=b, y=0, xend=b, yend=1/(b - a),linetype = "dashed") +
    theme_bw()+
    annotate("rect", 
           xmin = 25, 
           xmax = 45,
           ymin = 0,
           ymax = 1/40,
           fill = "blue", alpha=0.5) 

```

> (e) This is a continuous RV. Hence, $P[X=22.5]=0$.


\newpage

2. Calculate the following Probabilities from using a standard Normal distribution, $Z$ $\sim$ N(0,1).


> a. $P[Z < 0]$.

>> A: Using table, $P[Z < 0]=0.5$.

> b. $P[Z < -1.5]$.

>> A: Using table, $P[Z < -1.5]=0.0668$.

> c. $P[Z > 1]$.

>> A:  $P[Z > 1]\stackrel{\text{Compliment R}}{=} 1- P[Z \leq 1]= 1- 0.8413=0.1587$.


> d. $P[Z > -1.44]$.

>> A:  $P[Z > -1.44]\stackrel{\text{Compliment R}}{=} 1- P[Z \leq -1.44]= 1- 0.0749=0.9251$.

> e. $P[Z > 3.09]$.

>> A:  $P[Z > 3.09]\stackrel{\text{Compliment R}}{=} 1- P[Z \leq 3.09]= 1- 0.9990=0.001$.

> f. $P[-0.71 < Z < 0.92]$.

>> A: $P[-0.71 < Z < 0.92]=P[Z<0.92]-P[Z<-0.71]=0.8212-0.2389=0.5823$. Why? See below:

>> This is what we want:

```{r, echo=F,out.width="70%",fig.align = 'center'}
library(ggplot2)
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "steelblue",
                xlim = c(-0.71, 0.92), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3,-0.71, 0, 0.92, 3),
                     labels = c(-3, -0.71,0, 0.92, 3),
                     limits = c(-3, 3)) 

```
>> We note that P[Z<0.92] would be the red area on this plot: 

```{r, echo=F,out.width="70%",fig.align = 'center'}
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "red",
                xlim = c(-3, 0.92), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3, 0, 0.92, 3),
                     labels = c(-3, 0, 0.92, 3),
                     limits = c(-3, 3)) 

```

>> We also note that P[Z<-0.71] would be the green area on this plot: 

```{r, echo=F,out.width="70%",fig.align = 'center'}
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "green",
                xlim = c(-3,-0.71), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3,-0.71, 0, 3),
                     labels = c(-3, -0.71,0,  3),
                     limits = c(-3, 3)) 

```

>> If I get rid of the green area in the red area, what I am left with would be the blue area. 

```{r, echo=F,out.width="70%",fig.align = 'center'}
ggplot(data = data.frame(x = c(-3, 3)), aes(x)) + xlab("Z")+
  stat_function(fun = dnorm, n = 101, args = list(mean = 0, sd = 1)) + ylab("") +
  scale_y_continuous(breaks = NULL)+
   stat_function(fun = dnorm,
                geom = "area",
                fill = "green",
                xlim = c(-3,-0.71), alpha=0.5) +
  stat_function(fun = dnorm,
                geom = "area",
                fill = "steelblue",
                xlim = c(-0.71,0.92), alpha=0.5) +
    theme_bw()+
  scale_x_continuous(breaks = c(-3,-0.71, 0, 0.92, 3),
                     labels = c(-3, -0.71,0, 0.92, 3),
                     limits = c(-3, 3)) 

```

> g. $P[-1.5 < Z < -1.44]$.

>> A: $P[-1.5 < Z < -1.44]=P[Z<-1.44]-P[Z<-1.5]=0.0749-0.0668=0.0081$.

> h. $P[Z < -0.71$ or $Z > 0.92]$.

>> A: $P[Z < -0.71 \cup Z > 0.92] = P[Z < -0.71] + P[Z > 0.92] -P[Z < -0.71 \cap Z > 0.92]$. There is no common Z in the intersection, i.e $P[Z < -0.71 \cap Z > 0.92]=0$. Hence:

\begin{align}
P[Z < -0.71 \cup Z > 0.92] &= P[Z < -0.71] + P[Z > 0.92] \notag\\
&= P[Z < -0.71]+1- P[Z \leq 0.92] \notag\\
&=0.2389+1-0.8212\notag\\
&= 0.4177 \notag
\end{align}

\newpage

3. Find values of $z$ such that:

> a. The area to the left is 0.0202.

>> A: We are looking for the $z$ such that $P(Z<z)=0.0202$. We go to the table and find probability 0.0202 and then find the $z$ value. $z=-2.05$.

> b. The area to the left is 0.7517.

>> A: We are looking for the $z$ such that $P(Z<z)=0.7517$. We go to the table and find probability 0.7517 and then find the $z$ value. $z=0.68$.


> c. The area to the right is 0.025.

>> A: We are looking for the $z$ such that $P(Z>z)=0.025$. Table only have $P(Z\leq z)$ probabilities. So we need to convert it to something in that form. We note that $P(Z>z)=1-P(Z\leq z)$. Therefore, $1-P(Z\leq z)=0.025 \rightarrow P(Z\leq z)=1-0.025=0.975$. We go to the table and find probability 0.975 and then find the $z$ value. $z=1.96$.

> d. The area to the right is 0.3015.

>> A: We are looking for the $z$ such that $P(Z>z)=0.3015$. $1-P(Z\leq z)=0.3015 \rightarrow P(Z\leq z)=1-0.3015=0.6985$. We go to the table and find probability 0.6985 and then find the $z$ value. $z=0.52$.

\newpage
